A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-10 4_method.tex
redefine beading strategy mathematically
The old definition was for the specific beading strategy I was working on, rather than for beading strategies in general.

@@

The function $b$ should adhere to several criteria:
\begin{itemize}
\item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
\item $b$ is monotonic
%the item below follows from the two above
% \item between a location with radial distance $R(v) \in [\frac12 n\win, \frac12 (n+1)\win]$ (for integer $n$) there is only one transition to a different number of beads
\item $ 0 \leq b(d) \leq d / w_\text{min} $
\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\end{itemize}

For our method we also require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.

@@

We introduce a function which produces the $d$ at which all widths are prefered: 
\begin{align}
p(n) =
  \begin{cases} 
   \frac12 \wout & \text{if } n = \frac12 \\
    \wout + (n - 1) \win       & \text{otherwise}
  \end{cases}
\end{align}
We call a distance $d$ `prefered' when $d = p(b(d))$

>>>>

We define a beading strategy as the following set:
$$
\left\{ b(d), p(n), W(n, d), L(n, d), t, \alpha_{\text{max}} \right\}
$$
where
$b(d)$ gives the optimal bead count to cover a total distance of $d$,
$p(n)$ gives the optimal total distance of a given bead count $n$,
$W(n, d)$ gives the sequence of bead widths to cover a distance $d$ using $n$ beads,
$L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
$t$ is the length of transitions within which we switch to a different number of beads
and
$\alpha_{\text{max}}$ is the limit bisector angle of the significance measure.

We call a distance $d$ `prefered' when $d = p(b(d))$
For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.

The following restrictions hold:
\begin{itemize}
\item $tb(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0$
\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
%\item $b \left( p(n) \right) = n$ % follows from the above!
\item $b(d)$ is monotonic: $ b(d) \leq b(d + \epsilon)$
\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\end{itemize}

The angle requirement ansures that there is never a 3-way junction of significant bones.

By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading, which is defined as the following set:
$$
\left\{ d, w_i, l_i  \right\}
$$
where
$d = 2 R(v)$ is the total distance associated with $v$,
$w_i$ is the bead width of the bead with index $i$
end
$l_i$ is the distance of the toolpath location of bead $i$ from the outline.

\subsubsection{Proposed optimal beading strategy}
\todo{This section is about some optimal strategy which hasn't been fully developed (yet?).}

\todo{This section still formules the beading strategy in terms of radius instead of diameter, which halves the $n$ values.}

@@

The function $b$ should adhere to several criteria:
\begin{itemize}
\item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
%\item $b$ is monotonic
%the item below follows from the two above
% \item between a location with radial distance $R(v) \in [\frac12 n\win, \frac12 (n+1)\win]$ (for integer $n$) there is only one transition to a different number of beads
\item $ 0 \leq b(d) \leq d / w_\text{min} $
%\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\end{itemize}

@@

We introduce a function which produces the $d$ at which all widths are prefered: 
\begin{align}
p(n) =
  \begin{cases} 
   \frac12 \wout & \text{if } n = \frac12 \\
    \wout + (n - 1) \win       & \text{otherwise}
  \end{cases}
\end{align}
